---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# demoadbcplyr

<!-- badges: start -->
<!-- badges: end -->

The goal of demoadbcplyr is to be a proof-of-concept for the hardest possible use of dbplyr generating SQL to send to an ADBC driver. This example uses the ADBC FlightSQL driver, which itself wraps a connection to DuckDB. The proof-of-concept here uses dbplyr with a DBI connection that is pretending to be Postgres for just long enough to generate Postgres-flavoured SQL.

## Installation

You can install the development version of demoadbcplyr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("paleolimbot/demoadbcplyr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# Start the FlightSQL test server with `docker compose up`

library(demoadbcplyr)
library(dplyr, warn.conflicts = FALSE)

Sys.setenv(R_WRAPPER_FLIGHTSQL_TEST_URI = "grpc+tls://localhost:31337")
con <- wrapper_test_con()
tbl(con, "NATION") |> 
  arrange(n_nationkey)
```
